The corona of a fully convective star with a near-polar flare

### 2023-12-19 src/tex/ms.tex
[showyourwork] overleaf sync

From the \textit{XMM-Newton} EPIC spectra, we could measure the coronal properties of TIC~277 in both its quiescent, and flaring states~(Table~\ref{tab:specfit}). The resulting fit for the full data set~(Fig.~\ref{fig:spec_joint_all}) consists of a cooler and a hotter component of about \Tcool and \Thot\hspace{-1.cm}, respectively. Assuming these temperatures as ground truth, we also fitted 2T APEC models to the flaring and quiescent portions of the observations separately. The coronal temperatures did not update significantly using either subset. However, the emission measure weighted mean temperature $T_{\rm mean}$ changed from \Tqmean in the quiescent spectrum to \Tfmean in the flaring spectrum, since the hot component became more much dominant during the flare. From the quiescent PN spectra, we then also calculated soft X-ray flux of $F_X=$\FX, and a luminosity $L_X=$\LXquiet in the $0.2$-$2.0\,$keV band. %This suggests that the flaring corona emits the hotter component, while the cooler component corresponds to the quiescent corona. In this interpretation, the presence of a hot component in the quiescent spectrum indicates that TIC 277 is flaring below the detection threshold, consistent with an extrapolation of the flare frequency distribution to lower temperatures~(see the following Section, and Fig.~\ref{fig:ffd}).

We note that not using the full set of observations as ground truth resulted in an unconstrained hot coronal component during the flare. This can be interpreted as due to a lack of X-ray flux above $5\,$keV. Hot flares with temperatures of $>50\,$MK have been measured on DS~Tuc~A~\citep{pillitteri2011xray}. On the Sun, the highest flare associated coronal temperatures are around $35\,$MK~\citep{kay2003soft}.

>>>>

From the \textit{XMM-Newton} EPIC spectra, we could measure the coronal properties of TIC~277 in both its quiescent, and flaring states~(Table~\ref{tab:specfit}). The resulting fit for the full data set~(Fig.~\ref{fig:spec_joint_all}) consists of a cooler and a hotter component of about \Tcool and \Thot\hspace{-1.cm}, respectively. Assuming these temperatures \textcolor{red}{for the prior distribution}, we also fitted 2T APEC models to the flaring and quiescent portions of the observations separately. The coronal temperatures did not update significantly using either subset. However, the emission measure weighted mean temperature $T_{\rm mean}$ changed from \Tqmean in the quiescent spectrum to \Tfmean in the flaring spectrum, since the hot component became more much dominant during the flare. From the quiescent PN spectra, we then also calculated soft X-ray flux of $F_X=$\FX, and a luminosity $L_X=$\LXquiet in the $0.2$-$2.0\,$keV band. %This suggests that the flaring corona emits the hotter component, while the cooler component corresponds to the quiescent corona. In this interpretation, the presence of a hot component in the quiescent spectrum indicates that TIC 277 is flaring below the detection threshold, consistent with an extrapolation of the flare frequency distribution to lower temperatures~(see the following Section, and Fig.~\ref{fig:ffd}).

We note that not using the full set of observations as the prior resulted in an unconstrained hot coronal component during the flare. This can be interpreted as due to a lack of X-ray flux above $5\,$keV. Hot flares with temperatures of $>50\,$MK have been measured on DS~Tuc~A~\citep{pillitteri2011xray}. On the Sun, the highest flare associated coronal temperatures are around $35\,$MK~\citep{kay2003soft}.
